---
title: "Sessions"
format: html
---

The sessions are sorted from new to old.

```{r}
#| include: false
library(tidyverse)
library(DT)
library(stringr)
library(knitr)

# Load dataset
scores <- read_csv(file.path("data", "scores.csv"))
```

```{r}
#| include: false
#| echo: false

dates <- scores %>%
  arrange(desc(date)) %>%
  distinct(date) %>%
  pull(date)
```


```{r}
#| echo: false
#| results: asis

# it works, idk why, please dont touch

tmp_files <- purrr::map2(
  dates,
  seq_along(dates),
  ~ {
    tmp <- tempfile(fileext = ".qmd")
    formatted_date <- format(as.Date(.x), "%d.%m.%Y")
    cat(
      paste0(
        "## ", formatted_date, "\n\n",
        "```{r}\n",
        "#| echo: false\n\n", 
        "current_date = dates[", .y, "]\n\n",
        "day_scores <- scores %>%\n",
        "  filter(date == current_date) %>%\n",
        "  group_by(player) %>%\n",
        "  mutate(\n",
        "    total_strikes = sum(strikes, na.rm = TRUE),\n",
        "    avg_score = mean(score, na.rm = TRUE),\n",
        "    sd_score = sd(score, na.rm = TRUE)\n",
        "  ) %>%\n",
        "  ungroup() %>%\n",
        "  select(-c(strikes, drunk, date)) %>%\n",
        "  pivot_wider(names_from = round, values_from = score, names_glue = 'Round {round}') %>%\n",
        "  mutate(across(where(is.numeric), \\(x) round(x, 1))) %>%\n",
        "  mutate(player = str_to_title(player)) %>%\n",
        "  relocate(c(avg_score, sd_score, total_strikes), .after = last_col()) %>%\n",
        "  arrange(desc(avg_score)) %>%\n",
        "  rename(\n",
        "    Player = player,\n",
        "    Strikes = total_strikes,\n",
        "    'Average Score' = avg_score,\n",
        "    'Score Standard Deviation' = sd_score\n",
        "  )\n\n",
        "datatable(day_scores,\n",
        "  options = list(\n",
        "    dom = 't',\n",
        "    paging = FALSE,\n",
        "    searching = FALSE,\n",
        "    info = FALSE,\n",
        "    lengthChange = FALSE,\n",
        "    columnDefs = list(list(orderSequence = c('desc','asc'), targets = '_all'))\n",
        "  )\n",
        ")\n",
        "```\n"
      ),
      file = tmp
    )
    tmp
  }
)

# include all child documents and **print the result** so Quarto executes the chunks
purrr::walk(tmp_files, ~ cat(knitr::knit_child(.x, quiet = TRUE)))

```

